### 2019-03-22 Introduction.tex
Updates from Overleaf

At prediction time, one seeks to find the sequence with the highest probability $\mathbf{s}^*=\arg\max_\mathbf{s} p(\mathbf{s}|x)$, and this is usually implemented approximately with a beam search procedure \cite{lowerre1976harpy} (we modified into Algorithm \ref{alg:beam_combine}). The sequence history is encoded with an internal memory vector $h_t$ which is updated over time. RNN is also often equipped with the attention mechanism \cite{DBLP:journals/corr/BahdanauCB14}, which in each  timestep $t$ puts different weights on different words (features) and effectively attends on a list of important words $f_t$. The selected words $f_t$, the RNN memory $h_t$ at timestep $t$, and the previous label ${s_{t-1}}$ are concatenated and used to model the label probability distribution at time $t$ as $p(s_t|x,s_1,s_2,...,s_{t-1}) \sim  \softmax(\phi(f_t,h_t,s_{t-1}))$, where $\phi$ is a non-linear function, and $\softmax$ is the normalized exponential function generalizing binary logistic regression. \kechen{double check attention} %Other variants of RNN, such as sequence to sequence encoder-decoder structure \cite{DBLP:conf/emnlp/ChoMGBBSB14,DBLP:conf/nips/NamMKF17}, further take into account the word order in the documents. \kechen{remove last sentence?}

@@

In training, one needs to  schedule the transition among these objectives, a rather tricky endeavor. At prediction time, one needs to find the most probable set. This is done by (approximately) finding the most probable sequence $\mathbf{s}^*=\arg\max_\mathbf{s} p(\mathbf{s}|x)$ and treating it as a set $\hat{\mathbf{y}}=set(\mathbf{s}^*)$. With a large number of sequences, it is quite possible that the argmax has actually a low probability, which can lead to neglecting important information when we ignore sequences other than the top one. 
% containing all labels in the sequence $s^*$ as the predicted set.

>>>>

At prediction time, one seeks to find the sequence with the highest probability $\mathbf{s}^*=\arg\max_\mathbf{s} p(\mathbf{s}|x)$, and this is usually implemented approximately with a beam search procedure \cite{lowerre1976harpy} (we modified into Algorithm \ref{alg:beam_combine}). The sequence history is encoded with an internal memory vector $h_t$ which is updated over time. RNN is also often equipped with the attention mechanism \cite{DBLP:journals/corr/BahdanauCB14}, which in each timestep $t$ puts different weights on different words (features) and thus effectively attends on a list of important words. \kechen{The context vector $c_t$ is computed as the weighted average over the dense representation of the words.} The selected words $c_t$, the RNN memory $h_t$ at timestep $t$, and the previous label ${s_{t-1}}$ are concatenated and used to model the label probability distribution at time $t$ as $p(s_t|x,s_1,s_2,...,s_{t-1}) \sim  \softmax(\phi(c_t,h_t,s_{t-1}))$, where $\phi$ is a non-linear function, and $\softmax$ is the normalized exponential function generalizing binary logistic regression. %Other variants of RNN, such as sequence to sequence encoder-decoder structure \cite{DBLP:conf/emnlp/ChoMGBBSB14,DBLP:conf/nips/NamMKF17}, further take into account the word order in the documents. \kechen{remove last sentence?}

@@

In training, one needs to  schedule the transition among these objectives, a rather tricky endeavor. At prediction time, one needs to find the most probable set. This is done by (approximately) finding the most probable sequence $\mathbf{s}^*=\arg\max_\mathbf{s} p(\mathbf{s}|x)$ and treating it as a set $\hat{\mathbf{y}}=set(\mathbf{s}^*)$. With a large number of sequences, it is quite possible that the argmax has actually a low probability, which can lead to neglecting important information when we ignore sequences other than the top one.

% containing all labels in the sequence $s^*$ as the predicted set.
